Summary Tables

### 2020-02-25 summary_tables_outcomes.Rmd
Use qualified package name with select function
Use more self explanatory scenario names

scen_names_w_baseline <- append('baseline', scen_names)
scen_lt <- data.frame("scen_name" = names(io$accra$outcomes$whw), "val" = scen_names_w_baseline, stringsAsFactors = FALSE)

@@

      var <- scen_lt %>% filter(scen_name == cs) %>% select(val) %>% as.character()

@@

   #print(var)

@@

@@

      td4[, 2] <- round((td4[,3] / td4[,2] ) * 100000, 4)
      # / sum(io[[city]]$demographic$population, na.rm = T)

>>>>

scen_names_w_baseline <- c('bl', 'w_sc', 'bi_sc', 'car_sc', 'mc_sc', 'bus_sc')
scen_lt <- data.frame("scen_name" = names(io$accra$outcomes$whw), "val" = scen_names_w_baseline, stringsAsFactors = FALSE)

@@

      var <- scen_lt %>% filter(scen_name == cs) %>% dplyr::select(val) %>% as.character()

@@

@@

      var <- scen_lt %>% filter(scen_name == cs) %>% dplyr::select(val) %>% as.character()

      names(td4)[2] <- var

@@

      td4[, 2] <- round((td4[,3] / ( td4[,2] )) * 100000, 4)
      # / sum(io[[city]]$demographic$population, na.rm = T)
